Software Citation Principles

### 2016-07-20 sc-principles/rebuttal/rebuttal.tex

\textbf{Our response:}
We agree with Reviewer 2 on this issue, as this represents more of a position paper than an experimental paper.
That said, we would be willing to add an explicit research question and discuss the ``experimental'' design if required, but feel this would be an artificial construct that doesn't add much to the paper.

\item \textbf{Comment:}
\emph{I suggest to include one or more appendixes with all the details about the use cases presented. This would make the paper more self-contained.}

\textbf{Our response:}
\niemnote{I will add the full use cases text as an appendix, and revise to match the numbering in the table}
\niemnote{I will also add the FORCE16 comments and responses}

\niemnote{Dan \& Arfon: could you assist with adding descriptions to some of the use cases that don't have one?} \katznote{In both the Google doc and the appendix I think?}

@@

\niemnote{This will be addressed somewhat by the changes discussed above; but Dan, could you help with this?}

\item \textbf{Reviewer comment:}
\emph{It is not clear whether the authors consider software citations to be just the first step towards a long-term vision, or whether they consider software citations the overall final solution. It seems that the first is the case, but the long-term vision is not discussed.}

\textbf{Our response:}
\asnote{Perhaps we should be adding a short paragraph outlining how we believe that ultimately academic publishing should be moving towards sharing all of the products of researcher activity. This work is primarily about making software a citable entity which is just one part of a much larger change in the scholarly ecosystem.}

\niemnote{Dan, can you do this?} \katznote{I was hoping Arfon might do this one}

@@

\item \textbf{Reviewer comment:}
\emph{This paper doesn't have an experimental design in the strict sense, as it is more of a position paper than a research article. The PeerJ guidelines state that ``the submission should clearly define the research question'', which is currently not the case for this paper. However, I see a research question between the lines, which could be phrased as ``how can citations be applied to software products to account for their increasing importance in scientific research?''. By making such a research question explicit, the PeerJ requirements can be met.}

\textbf{Our response:}
\asnote{The reviewer's suggested text sounds pretty good to me. Perhaps drop/change 'scientific' in that sentence?}

\niemnote{Agreed on both counts}

\niemnote{Let's say that}
We agree that this paper is more of a position paper than research article, and thus that creating a research question would be an artificial construct. We are willing to make this change if required, but feel it wouldn't add much to the paper.
\katznote{and maybe add}
We have modeled our process on the work done by the FORCE2016 Data Citation group, which included publishing a PeerJ CS paper (\url{https://peerj.com/articles/cs-1/}) which has been written in a similar manner to our paper.

### 2016-07-20 sc-principles/software-citation-principles.tex
adding description to B.5 and google doc

>>>>

This case describes the need for a research who has contributed to software (by design, software engineering, development, testing, patching, documentation, training, evangelizing, etc.)
to have their software work recognized by their employer or colleagues for the purpose of career advancement and increased professional reputation.
